HW2

### 2017-12-04 hw2/main.tex
Add files via upload

Thus party one has minimum encrypted element between u \& v as required
\subsection*{\textbf{Description}}

>>>>

Thus party one has minimum encrypted element between u \& v as required
\subsection*{\textbf{Description}}
Pre-work
Set a bit length for u and v.\\
Phase 1:\\
	Goal:
    To compute whether u or v is the minimum\\

	Part 1:
	First,Party 1 chooses a function. Either greater than or less than.
	Next, for each bit, we compute a list of masks L.
	Next, we permute these masks to create L'.
    Party 1 sends L' to Party 2.\\

	Part 2:
	Party 2 decrypts L' to create M.
    If any of the elements in M equals 1, $\alpha$, else it equals 0. If 1 is present, we know the function chosen in the 		beginning is true.
    Party 2 then sends an encrypted copy of $\alpha$ \\

	Part 3:
	If alpha is 1, function is true. If alpha is 0, it is false. Map that to 0 if u is min, otherwise, map to 1.
    If F was u > v alpha already has 0 if u is min 1 if v
for the other function we have to subtract 1 and to get 0 if u is minimum 1, otherwise, return Epk(result)\\

Phase 2:\\
	Goal:
    To return the calculated minimum to the requesting party.\\

    First, Party 1 computes Epk(u), Epk(v), and MinIndice.
    Next, for each bit, Party 1 computes $\Gamma$ and $\Gamma'$.
    Lastly, Party 1 sends $\Gamma'$ and MinIndice to Party 2.\\

	Party 2 then decrypts the received MinIndice.
    With that and $\Gamma$, they compute $M_i'$.
    Party 2 then sends M' to Party 1.\\

    Party 1 then computes M from M'.
    With that, Party 1 is able to compute $\lambda$ and $\Gamma$.
    For each $\lambda$, Party 2 removes random terms from the differences so that the minimum can be found.
    If $\Gamma$ is returned when computing it, u is the minimum. otherwise, v is the minimum.\\
